Optimized Synthesized Spectrum

### 2016-10-09 paper/ms.tex
Update ms.tex

Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels.

@@

The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1). 
\bigskip

Because linear regression is sensitive to bad data points, extra parameters need to be added to describe the bad data points. Here we introduce \(\big\{q_n\big\}_{n=1}^{N}\), \(P\), \(Y\) and \(V\).

We need to find a correct objective function! 
\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
\bigskip

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
a+b+c should be equal to 1.
\bigskip

The code is as followed:
\bigskip

popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0, sigma=error)
\bigskip

parameters = popt
\bigskip

x\_data, y\_data and z\_data are \(y_{j-1,n}^{inferred},y_{j,n}^{inferred} \)

and \( y_{j+1,n}^{inferred}\)
\bigskip

>>>>

Suppose we have a trained model. The training set contains 548 stellar and each stellar spectrum has 8575 pixels. Every pixel is related to a specific wave length. It belongs to APOGEE release 10 and has a good quality. These stellar are the very same objects as used by the APOGEE survey for the calibration of DR10. Each of them has at least nine stellar labels. But in the training step, we only use three labels: $T_{eff}$, $log$ g  and $\left[Fe/H\right]$. They span the range of $3500K <T_{eff}< 5300K$, $0 <log$ $g< 5$ and $-2.5 <\left[Fe/H\right]< 0.45$.

@@

The method we use is to represent the spectrum at pixel j by using the inferred spectrum at pixel j-1,pixel j and pixel j+1.(If the pixel is out of range, set the flux as 1). The data we use is the same as the training step.
\bigskip

The objective function is linear :
\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]

And the Jacobian Matrix of the objective function with respect to parameters 
\[J = \left[y_{j-1,n}^{inferred}/\sigma_{j-1,n}, y_{j,n}^{inferred}/\sigma_{j,n},, y_{j+1,n}^{inferred}/\sigma_{j+1,n},\right]\]
Where $\sigma{j,n}$ is the uncertainty for pixel j of stellar n.
\bigskip

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is the least chi-squared method.
\bigskip

To obtain a,b and c, we introduce several matrix: Y, A and C. Here the numbers of stellar and pixel each star are $n-star$ and $n-pixel$

% insert matrix

\[
Y
=
\begin{bmatrix}
    Y_1&Y_2 &\dots&Y_{n-star}\\

\end{bmatrix}
\]

where
\[
 Y_n
=
\begin{bmatrix}
    y_{1,n} \\
    y_{2,n} \\
    \vdots  \\
    y_{j,n}  \\

\end{bmatrix}
\]

% A
\[
A
=
\begin{bmatrix}
    A_1&A_2 &\dots&A_{n-star}\\

\end{bmatrix}
\]

where
\[
A_n
=
\begin{bmatrix}

    1 & y_{1,n} ^{inferred} & y_{2,n} ^{inferred}\\
    y_{1,n}^{inferred}&y_{2,n}^{inferred}& y_{3,n}^{inferred}  \\
    \vdots & \vdots & \vdots \\
    y_{j-1,n}^{inferred}&y_{j,n}^{inferred}& 1  \\

\end{bmatrix}
\]

% sigma-C

\[
C
=
\begin{bmatrix}
    C_1&C_2 &\dots&C_{n-star}\\

\end{bmatrix}
\]

where
\[
C_n
=
\begin{bmatrix}

    \sigma_{1,n}&0&\dots&0\\
    0& \sigma_{2,n}&\dots&0 \\
    \vdots & \vdots & \vdots \\
    0&\dots&0&\sigma_{j,n}  \\

\end{bmatrix}
\]

$\sigma_{j,n} $is the uncertainty for pixel j of star n. 
\bigskip

We cut the matrix Y,A and C into n-star smaller matrix so the calculation speed is higher. To calculate a,b and c.

 \(X = 
 \begin{bmatrix}

    a\\
    b \\
    c \\

\end{bmatrix}
\)=$\sum_{n=1}^{n-star} X_n \over{n-star}$

where
\[
X_n = 
\begin{bmatrix}

    a_n\\
    b_n \\
    c_n \\

\end{bmatrix}
=\left[A_n^TC^{-1}_nA_n\right]^{-1}\left[A_n^TC^{-1}_nY_n\right]
\]
